DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2023-08-07 subsections/design/cavity/cavity.tex
thesis scripts added
design finished, simulation started
başlık eklendi

In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;

\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
    \begin{aligned}
        f_{107.5} = 107.5 \textrm{ MHz} \\
        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
        R_1 = \frac{R_2}{4} = 0.188 m \\
        h = \frac{\lambda}{2} = 1.394 m 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        f_{180} = 180 \textrm{ MHz} \\
        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
        R_1 = \frac{R_2}{4} = 0.113 m \\
        h = \frac{\lambda}{2} = 0.833 m 
    \end{aligned}
\end{eqnarray}

In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:107_simple_cavity_design}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst107_e.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst180_e.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:cst_simple_cavity_designs}
\end{figure}

As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish107mod.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish180mod.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson SUPERFISH field results of truncated cavities}
    \label{fig:107_180_modified_cavities_superfish}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=0.95\linewidth]{../../../figures/superfish/superfish107mod_z.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180mod_z.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
    \label{fig:180_cavity_shunt_diff}
\end{figure}

One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};

\begin{equation*}
    \begin{aligned}
        \Delta Z_{107.5}=2.5\%
    \end{aligned}
    \qquad
    \begin{aligned}
        \Delta Z_{180}=2.7\%
    \end{aligned}
\end{equation*}

>>>>

In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
    \begin{aligned}
        f_{107.5} = 107.5 \textrm{ MHz} \\
        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
        R_1 = \frac{R_2}{4} = 0.188 m \\
        h = \frac{\lambda}{2} = 1.394 m 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        f_{180} = 180 \textrm{ MHz} \\
        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
        R_1 = \frac{R_2}{4} = 0.113 m \\
        h = \frac{\lambda}{2} = 0.833 m 
    \end{aligned}
\end{eqnarray}
In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:107_simple_cavity_design}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst107_e.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst180_e.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:cst_simple_cavity_designs}
\end{figure}
As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish107mod.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish180mod.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson SUPERFISH field results of truncated cavities}
    \label{fig:107_180_modified_cavities_superfish}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=0.95\linewidth]{../../../figures/superfish/superfish107mod_z.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180mod_z.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
    \label{fig:180_cavity_shunt_diff}
\end{figure}
One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
\begin{equation*}
    \begin{aligned}
        \Delta Z_{107.5}=2.5\%
    \end{aligned}
    \qquad
    \begin{aligned}
        \Delta Z_{180}=2.7\%
    \end{aligned}
\end{equation*}

### 2023-08-07 subsections/design/first_design/first_design.tex
başlık eklendi

A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
    \label{fig:initial_design}
\end{figure}
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_design3.png}
      \caption{Axial cross section.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_design2.png}
      \caption{Cross section at acceleration plane.}
    \end{subfigure}
    \caption{Initial design of the proposed rhodotron.}
    \label{fig:initial_design_cross_section}
\end{figure}
The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.

\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_magnet_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_magnet_design2.png}
    \end{subfigure}
    \caption{Initial magnet design.}
    \label{fig:initial_magnet_design}
\end{figure}

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
    \caption{Magnetic field in acceleration plate of initial magnet design.}
    \label{fig:initial_magnet_design_B}
\end{figure}

\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.

After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
    \label{fig:initial_three_magnet_design}
\end{figure}

These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.

\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}[b]{.8\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/cst/cst_first_design4.png}
      \caption{One pass simulation of \fromfig{initial_design}}
    \end{subfigure}
    \centering
    \begin{subfigure}[b]{.8\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/cst/cst_second_design3.png}
      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
    \end{subfigure}
    \caption{$|r|$ vs $Energy$ simulation of initial design.}
    \label{fig:initial_designs_PIC_phase_space_monitor}
\end{figure}

The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.

@@

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}
    \caption{Magnetic field in acceleration plate of improved magnet design.}
    \label{fig:improved_magnet_design_B}
\end{figure}

From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.

>>>>

A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
    \label{fig:initial_design}
\end{figure}
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_design3.png}
      \caption{Axial cross section.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_design2.png}
      \caption{Cross section at acceleration plane.}
    \end{subfigure}
    \caption{Initial design of the proposed rhodotron.}
    \label{fig:initial_design_cross_section}
\end{figure}
The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_magnet_design1.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_magnet_design2.png}
    \end{subfigure}
    \caption{Initial magnet design.}
    \label{fig:initial_magnet_design}
\end{figure}

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
    \caption{Magnetic field in acceleration plate of initial magnet design.}
    \label{fig:initial_magnet_design_B}
\end{figure}
\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.

After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
    \label{fig:initial_three_magnet_design}
\end{figure}
These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}[b]{.8\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/cst/cst_first_design4.png}
      \caption{One pass simulation of \fromfig{initial_design}}
    \end{subfigure}
    \centering
    \begin{subfigure}[b]{.8\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/cst/cst_second_design3.png}
      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
    \end{subfigure}
    \caption{$|r|$ vs $Energy$ simulation of initial design.}
    \label{fig:initial_designs_PIC_phase_space_monitor}
\end{figure}
The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.

@@

\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}
    \caption{Magnetic field in acceleration plate of improved magnet design.}
    \label{fig:improved_magnet_design_B}
\end{figure}
From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.

### 2023-08-07 subsections/design/magnet/magnet.tex
başlık eklendi

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.

\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
    \end{subfigure}
    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
    \label{fig:magnet_design_illustrations}
\end{figure}

In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \caption{Trejectory of a particle in single pass}
    \label{fig:magnet_design}
\end{figure}

From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
\begin{eqnarray}
    L_{in} &=& 2R_2 \nonumber\\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
\end{eqnarray}

After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},

\begin{eqnarray}
    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
\end{eqnarray}

\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.

@@

Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
\begin{eqnarray*}
    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
    W_{total} &=& 394 keV \\
    \beta_{40keV} &\approx& 0.374 \\
    \beta_{394keV} &\approx& 0.825
\end{eqnarray*}
It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
\begin{eqnarray*}
    L_{pass} &=& K \\
    L_{in} + L_{out} &=& K
\end{eqnarray*}

Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
\begin{equation} \label{eq:mag_sweep_constraint}
    L_{out} = K
\end{equation}

To start, an optimization criteria for the following pass such as
\begin{itemize}
    \item Ensure the phase stability of the synchronous electron
    \item Maximize the energy gain of the synchronous electron
    \item Minimize the energy spread of the beam
    \item Minimize the phase lag spread of the beam
    \item All of the above with decided weights
\end{itemize}
needs be selected. Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.

>>>>

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
    \end{subfigure}
    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
    \label{fig:magnet_design_illustrations}
\end{figure}
In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \caption{Trejectory of a particle in single pass}
    \label{fig:magnet_design}
\end{figure}
From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
\begin{eqnarray}
    L_{in} &=& 2R_2 \nonumber\\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
\end{eqnarray}
After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
\begin{eqnarray}
    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
\end{eqnarray}
\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.

@@

Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
\begin{eqnarray*}
    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
    W_{total} &=& 394 keV \\
    \beta_{40keV} &\approx& 0.374 \\
    \beta_{394keV} &\approx& 0.825
\end{eqnarray*}
It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
\begin{eqnarray*}
    L_{pass} &=& K \\
    L_{in} + L_{out} &=& K
\end{eqnarray*}
Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
\begin{equation} \label{eq:mag_sweep_constraint}
    L_{out} = K
\end{equation}
To start, an optimization criteria for the following pass such as
\begin{itemize}
    \item Ensure the phase stability of the synchronous electron
    \item Maximize the energy gain of the synchronous electron
    \item Minimize the energy spread of the beam
    \item Minimize the phase lag spread of the beam
    \item All of the above with decided weights
\end{itemize}
needs be selected. Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
